Live Functional Programming with Typed Holes

### 2018-04-09 calculus.tex
write down my cite guideline
typo: remove extra word

@@

We supplement each expression hole from \Hazelnut with such a
hole \emph{name}, which are new to \HazelnutLive; an empty hole is
written $\hehole{u}$, where $u$ is a unique name for the hole.
%
Rule {SEHole}\todo{rule name macros}{} specifies that an empty hole synthesizes hole type, written $\tehole$.
%
If an empty hole appears where an expression of some other type is
expected, e.g. under an explicit ascription (governed by Rule {SAsc})
or in the argument position of a function application (governed by
Rule {SAp}, discussed below), we apply the \emph{subsumption rule},
Rule {ASubsume}, which specifies that if an expression $e$ synthesizes
type $\htau$, then it can be checked against any \emph{consistent}
type, $\htau'$.

>>>>

% 10. Citations in this Names+Year form break sentence and paragraph
% flow for the reader, sometimes quite severly.  Put long citation
% chains at the ends of sentences (or better yet, in their own little
% paragraph, as I did below).

@@

We supplement each expression hole from \Hazelnut with a
hole \emph{name}, which are new to \HazelnutLive; an empty hole is
written $\hehole{u}$, where $u$ is a unique name for the hole.
%
Rule {SEHole}\todo{rule name macros}{} specifies that an empty hole synthesizes hole type, written $\tehole$.
%
If an empty hole appears where an expression of some other type is
expected, e.g. under an explicit ascription (governed by Rule {SAsc})
or in the argument position of a function application (governed by
Rule {SAp}, discussed below), we apply the \emph{subsumption rule},
Rule {ASubsume}, which specifies that if an expression $e$ synthesizes
type $\htau$, then it can be checked against any \emph{consistent}
type, $\htau'$.
